Fast and Error-Adaptive Count-Distinct Sketch \\for Influence Maximization

### 2020-12-18 paper.tex
Update on Overleaf.

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{subfiles}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{subfig}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
\usepackage{booktabs}
\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}
%%%%%%
% Notes: 
% plot grouping/hue +
% table smallcaps +
% Time score memory center +
% Abstract
% Differences between infuser and us+
% time skecth diff between us +
% neden 0.005 +
% active vertex colors +
%%%%%
\ifCLASSOPTIONcompsoc
  \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

@@

Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm\cite{flajolet1985probabilistic} can estimate the cardinality of distinct elements in reachability sets with a constant number of registers($M$), and most importantly union of these sets can be done in a constant number of operations.

Flajolet–Martin sketch only stores how rare elements are in a multi-set.The rarity of the elements is often computed by counting leading zeros in the item's hash values.  The registers are initialized with zero values in beginning. Items are added by storing the longest leading zero count. Cardinality estimation can be done by taking 2 to the power of the stored value. Multiple registers and hash functions, $M[j]$ and $h_j$, are commonly used to reduce variance.
Adding item $x$ to register $M$, and its result $M'$ is shown in equation~\ref{eq:sketch-add}.

@@

The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
The edge $\{u,v\}$ is exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$. One of the benefits of this approach is, sampling an edge is only single XOR and compare-greater-than operations. Also, the following control flow branch can be removed using conditional move operations. 
An efficient implementation of this approach will be discussed later in this section.
\begin{figure}[!ht] 
    \centering
    \includegraphics[width=1\linewidth]{./images/cdf.pdf}
    \caption{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}
    \label{fig:prob-cdf} 
\end{figure}
Using a strong hash function such as {{\sc Murmur3}} ensures all bits independently change if the input is changed. This property allows us to generate good enough pseudo-random values for fair sampling. To prove the fairness of random values generated with the hash-based approach, we generated a large number of samples for various real-life networks and graphed the bias of random values $P(u,v)_r$ used while sampling.

@@

Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
After adding vertices to the seed set, \acro perform Monte-Carlo simulations to estimate the reachability of the latent seed set.
The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{g}$, and the marginal gain estimation error after the last sketch larger than local threshold $\epsilon_{l}$. Before rebuilding stale sketches, the reachability set of latent seed set is marked as visited, and considered blocked in their respective simulations while rebuilding the sketches. Two threshold values allow the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. If a rebuild is not required, only the last added vertex's sketch is also merged with $mask$ to update $R_G(S)$.

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{subfiles}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{subfig}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
\usepackage{booktabs}
\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}
%%%%%%
% Notes: 
% plot grouping/hue +
% table smallcaps +
% Time score memory center +
% Abstract
% Differences between infuser and us+
% time skecth diff between us +
% neden 0.005 +
% active vertex colors +

% GRID PARAM SEARCH
% Performance comparison vs others (why slowed down?)
% Error-Adaptive rebuilding sat
%%%%%
\ifCLASSOPTIONcompsoc
  \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

@@

Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm\cite{flajolet1985probabilistic} can estimate the cardinality of distinct elements in reachability sets with a constant number of registers($J$), and most importantly union of these sets can be done in a constant number of operations.

Flajolet–Martin sketch only stores how rare elements are in a multi-set.The rarity of the elements is often computed by counting leading zeros in the item's hash values.  The registers are initialized with zero values in beginning. Items are added by storing the longest leading zero count. Cardinality estimation can be done by taking 2 to the power of the stored value. Multiple registers and hash functions, $M[j]$ and $h_j$, are commonly used to reduce variance.
Adding item $x$ to sketch $M$, and its result $M'$ is shown in equation~\ref{eq:sketch-add}.

@@

% The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
The edge $\{u,v\}$ is exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$. One of the benefits of this approach is, sampling an edge is only single XOR and compare-greater-than operations. Also, the following control flow branch can be removed using conditional move operations. 
An efficient implementation of this approach will be discussed later in this section.
\begin{figure}[!ht] 
    \centering
    \includegraphics[width=1\linewidth]{./images/cdf.pdf}
    \caption{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}
    \label{fig:prob-cdf} 
\end{figure}
Using a strong hash function such as {{\sc Murmur3}} ensures all bits independently change if the input is changed. This property allows us to generate good enough pseudo-random values for fair sampling. To prove the fairness of random values generated with the hash-based approach, we generated a large number of samples for various real-life networks and graphed the bias of random values $P(u,v)_r$ used while sampling.

@@

Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{g}$, and the marginal gain estimation error after the last sketch is larger than local threshold $\epsilon_{l}$. Before rebuilding stale sketches, the reachability set of latent seed set is marked as visited, and considered blocked in their respective simulations while rebuilding the sketches. Two threshold values allow the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. If a rebuild is not required, only the last added vertex's sketch is also merged with $mask$ to update $R_G(S)$.
